### 2014-12-15 README.Rmd
updated readme with new links to ttutorial page on our site

The `taxize` tutorial is can be found at [http://ropensci.org/tutorials/taxize_tutorial.html](http://ropensci.org/tutorials/taxize_tutorial.html)

@@

For more examples see the [tutorial](http://ropensci.org/tutorials/taxize_tutorial.html)

@@

>>>>

The `taxize` tutorial is can be found at [http://ropensci.org/tutorials/taxize.html][tut].

@@

For more examples see the [tutorial][tut]

@@

[tut]: http://ropensci.org/tutorials/taxize.html
